### 2015-07-13 implementation-specs.tex
neg vspace in table 1 and 2
Submitted version
Address reviewer comment on awkward sentence.

\begin{figure}
\begin{grammar}
  <spec>         ::= <id> [ constraints ]

@@

Recall that Spack guarantees there will be only a single version of any package in
the spec DAG.  Therefore, within the same DAG, each dependency can be uniquely identified by
only its package name.  The user does not have to think about DAG connectivity to add
constraints.  She need only know that a package depends, somehow, on {\tt callpath}.
For the same reason, the constraint order does not matter; dependency constraints
can appear in arbitrary order.

@@

{\bf Versions.}
The version constraint, denoted with {\tt @}, was already covered above. Versions
can be precise ({\tt @2.5.1}) or denote a range ({\tt @2.5:4.4}),
which may be open-ended ({\tt @2.5:}).

>>>>

\begin{figure}
\begin{grammar}\small
  <spec>         ::= <id> [ constraints ]

@@

Recall that Spack guarantees there will be only a single version of any package in
the spec DAG.  Therefore, within the same DAG, each dependency can be uniquely identified by
only its package name.  The user does not have to think about DAG connectivity to add
constraints.  She only needs to know that a package somehow depends on {\tt callpath}.
For the same reason, the constraint order does not matter; dependency constraints
can appear in arbitrary order.

@@

{\bf Versions.}
Version constraints, denoted with {\tt @}, were already covered above. Versions
can be precise ({\tt @2.5.1}) or denote a range ({\tt @2.5:4.4}),
which may be open-ended ({\tt @2.5:}).
